Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-12 Arxiv/main.tex
Update Arxiv/main.tex
fix typos
update figures

\section{Mechanism Proposition}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
Notice that $\candidateset$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

@@

\subsection{$\hexpmech$ Proposition}

@@

  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved.
\end{proof}

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is provided by its probability density function:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t}{b}},
\end{equation*}
where $Y \thicksim Lap(b)$, $b = \frac{\Delta \bysinfer}{\epsilon}$ in our case.

@@

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[data size range from 50 to 100]{
    \includegraphics[width=0.4\textwidth]{global_epsilon_size50to100.eps}}
  \subfigure[data size range from 100 to 200]{
    \includegraphics[width=0.4\textwidth]{global_epsilon_size100to200.eps}} 
  % \subfigure[data size range from 200 to 500]{
  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size200to500.eps}} 
  % \subfigure[data size range from 500 to 1000]{
  %   \includegraphics[width=0.23\textwidth]{global_epsilon_size500to1000.eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure}

$\epsilon = 1.0$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound. That is to say, we achieved a higher privacy level than expected. In next step, we are going to improve the accuracy using this property.

>>>>

\section{Mechanism Proposition}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section \ref{sec_background}.
Notice that $\candidateset$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

@@

\subsubsection{$\hexpmech$ Proposition}

@@

  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved.

@@

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is provided by its probability density function:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}},
\end{equation*}
where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.

@@

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism. By applying the accuracy bound into Hellinger distance in our case:
$$
\begin{array}{rcl}
& Pr[\hlg(\bysinfer(\dataobs), r_L ) = \hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
\end{array}
$$
where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor$.\\
By simplification the Hellinger distance in $\hlg(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
\begin{itemize}
\item[\textbf{case 1:}] \textbf{t is even}\\

\item[\textbf{case 2:}] \textbf{t is odd}
\end{itemize}

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.6\textwidth]{privacyloss.eps}
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 1.0$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure}

$\epsilon = 1.0$ is a privacy upper bound, we can observe that the concrete $\epsilon$ values are smaller than the upper bound. That is to say, we achieved a higher privacy level than expected.
